---
title: "Tidy-Progamming"
description: "tidyverse()"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r knitsetup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, out.width = "100%")
```

```{r packages, include=FALSE}
library(kableExtra)
library(tidyverse)
library(cccolr)
```

```{r options, include=FALSE}
theme_set(theme_light() +
    theme(
        strip.background = element_rect(fill = "#98D8DC"),
        strip.text = element_text(colour = "#FFFFFF")
    )
)
```

<!-- start ---------------------------------------------------------------- -->
# What does `tidy` mean?

Like you were supposed to tidy up your room being a child, you should use tidy coding/programming being a Biostatistician. To do so, you should get yourself familiar with the `tidyverse`.

The main difference between `base R` and `tidyverse` is the way the code is organized and the use of **tibbles** instead of **data.frames**. While tibbles consist of data.frame, which is familiar to any baseR-Programmer, tibbles consists of multiple  other features which allow a smooth handling regarding data management (data wrangling) or statistical analysis.


# What is the `tidyverse()`?

The `tidyverse` is a collection of R packages, that were developed by Hadley Wickham to harmonize R languages. Designed to do data science, all packages share an underlying design philosophy, grammar, and data structures. If you want to read more, check out the webpage [https://www.tidyverse.org/](https://www.tidyverse.org/).

Like any other R-package, you can install tidyverse as follows:

```{r, eval=FALSE}
install.packages("tidyverse") # install tidyverse
library(tidyverse) #load tidyverse
```


# tidy Programming

Within the tidyverse, single programming steps can be executed subsequently using a pipe operator (`%>%`). Moreover, tidy-programming is based on verbs, representing actions that should be applied to the data. 

>**Tipp:** The short-key to write a pipe-operator is cmd + shift + m (Mac) and ctrl + shift + m (Windows).

# tidymodels()







<!-- end ------------------------------------------------------------------ -->

